Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-10-02 schedule.tex
add simple order flow

OAS

Most of the related methodologies can be archived into \textbf{four} main modules, namely \textit{Service Standardization}, \textit{Decision Making Support}, \textit{Matching Regulation} and \textit{Platform Assistance} which are going to explained in detail respectively.

>>>>

OAS  
\begin{figure}[!h]
\centering\small\resizebox{0.6\textwidth}{!}{\input{figures/order_flow}}
\caption{Primary Flow of Order}
\label{fig:orderflow}
\end{figure}
Most of the related methodologies can be archived into \textbf{four} main modules, namely \textit{Service Standardization}, \textit{Decision Making Support}, \textit{Matching Regulation} and \textit{Platform Assistance} which are going to explained in detail respectively.
